Arc Blanc: a real time ocean simulation framework

### 2024-11-12 paper.tex
Make notation more clear in interpolation degree calculation

More concretely, the velocity must be computed at any horizontal position in $I=[y_{min}, y_{max}]$.
In \framework, $N$ growing depths $y_i$ are chosen in this interval $I$.
For each of these depths $y_i$, the $i$-th velocity $\mathbf{v_i}(\mathbf x,y_i,t)$ is computed using one IFFT, leading to $N$ IFFTs for all the sampled depths $y_i$.
Then, the velocity $\mathbf{v}(\mathbf x,y,t)$ at any depth $y\in I$ is computed using an ad hoc interpolation from the different $\mathbf{v_i}$.

@@

\Framework uses the following logarithmic distribution:
\begin{equation}
	d(y_i) =
	\begin{cases}
		\beta \ln(\alpha|y_i|^2+1) ~~\text{if}~y_i>0     \\
		-\beta \ln(\alpha|y_i|^2+1) ~~\text{if}~y_i\leq0 \\
	\end{cases}
\end{equation}
where $\alpha=0.0001$ and $\beta = -y_{min}/\left(2 \ln(\alpha |y_{min}|^2 + 1)\right)$.

This distribution is designed based on the following considerations.
First, while the velocity decays exponentially, it relies on a logarithmic similar to $y_i\mapsto \ln(|y_i|+1)$.
Since this function transforms the negative $y_i$ into a positive one, the result is multiplied by the sign of $y_i$.
Also, this function decreases slowly (actually with $\ln(250+1)=5.5$), hence the logarithmic distribution uses the square of $|y_1|$.
Lastly, the parameter $\alpha$ controls the “squeezing” in the center, while the parameter $\beta$ controls the deepest value of $d$.
Notice that $\beta$ is chosen as the solution of $d(y_{min})=\frac{y_{min}}{2}$ but not at $y_{min}$: it is the solution giving the best accuracy after multiple tries.

@@

Moreover, using the logarithmic distribution leads to $d(y_{min})=\frac{y_{min}}{2}$.
Assuming that the velocity at $y_{min}$ is null, then for any depth between $y_{min}$ and $\frac{y_{min}}{2}$ the velocity can be computed between the one at $\frac{y_{min}}{2}$ and $0$.

>>>>

More concretely, the velocity must be computed at any horizontal position in $I=[y_{min}, y_{max}]$.
In \framework, $d$ growing depths $y_i$ are chosen in this interval $I$.
For each of these depths $y_i$, the $i$-th velocity $\mathbf{v_i}(\mathbf x,y_i,t)$ is computed using one IFFT, leading to $d$ IFFTs for all the sampled depths $y_i$.
Then, the velocity $\mathbf{v}(\mathbf x,y,t)$ at any depth $y\in I$ is computed using an ad hoc interpolation from the different $\mathbf{v_i}$.

@@

\Framework uses the following logarithmic distribution:
\begin{equation}
	l_d(y_i) =
	\begin{cases}
		\beta \ln(\alpha|y_i|^2+1) ~~\text{if}~y_i>0     \\
		-\beta \ln(\alpha|y_i|^2+1) ~~\text{if}~y_i\leq0 \\
	\end{cases}
\end{equation}
where $\alpha=0.0001$ and $\beta = -y_{min}/\left(2 \ln(\alpha |y_{min}|^2 + 1)\right)$.

This distribution is designed based on the following considerations.
First, while the velocity decays exponentially, it relies on a logarithmic similar to $y_i\mapsto \ln(|y_i|+1)$.
Since this function transforms the negative $y_i$ into a positive one, the result is multiplied by the sign of $y_i$.
Also, this function decreases slowly (actually with $\ln(250+1)=5.5$), hence the logarithmic distribution uses the square of $|y_1|$.
Lastly, the parameter $\alpha$ controls the “squeezing” in the center, while the parameter $\beta$ controls the deepest value of $l_d$.
Notice that $\beta$ is chosen as the solution of $l_d(y_{min})=\frac{y_{min}}{2}$ but not at $y_{min}$: it is the solution giving the best accuracy after multiple tries.

@@

Moreover, using the logarithmic distribution leads to $l_d(y_{min})=\frac{y_{min}}{2}$.
Assuming that the velocity at $y_{min}$ is null, then for any depth between $y_{min}$ and $\frac{y_{min}}{2}$ the velocity can be computed between the one at $\frac{y_{min}}{2}$ and $0$.
